---
title: "p8105 hw5"
author: "Weize Sun"
date: "11/20/2021"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

### Cleaning data

```{r}
homicide_df = 
  read.csv("./data/homicide-data.csv") %>% 
  janitor::clean_names() %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```


### Summarize number of homicides for each city

```{r}
aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```


### Run a prop.test for Baltimore

```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved), 
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>% 
  broom::tidy()
```

### Run prop.test for each city

```{r}
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```

### Draw a plot for the result

```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  labs(
    title = "Estimate and CIs for each city",
    x = "City of State",
    y = "Estimate rate",
    caption = "data from Washington Post")
```


## Problem 2

### combine all csv files to one data frame and tidy data


```{r}
file = list.files(path = "./data/data1")
path = str_c("./data/data1/", file)
arm_id  = str_remove(file, pattern = ".csv")

arm_df = 
  tibble(arm_id,
         data = map(.x = path, ~read_csv(.x))) %>% 
  unnest(cols = data) %>% 
  mutate(arm_and_id = arm_id) %>% 
  separate(arm_and_id, into = c("arm", "id"), sep = "_") %>% 
  relocate(arm_id, arm, id) %>% 
  mutate(arm = recode(arm, "con" = "control", "exp" = "experimental")) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "time",
    values_to = "observations") %>% 
  separate(time, into = c("omit", "week"), sep = "_") %>% 
  select(-omit)
```

### Make a spaghetti plot

```{r}
arm_df %>% 
  mutate(week = as.numeric(week)) %>% 
  ggplot(aes(x = week, y = observations, color = arm)) +
  geom_line(aes(group = arm_id), alpha = 0.5) +
  geom_smooth(se = FALSE) +
  labs(    
    title = "Observations on each subject over time",
    x = "Week",
    y = "Observations",
    caption = "Data from p8105 website"
  )
```

### Summary on result

From the plot above, we can see that generally the observation of experimental group is higher than control group. At the same time, the experimental line is increasing over time, while the control line is smooth, which means there are no big changes on observation over time.


